Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-22 ms.tex
omg

@@

\begin{figure}
\includegraphics[width=\columnwidth]{bh_growth.eps}
\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
  ($\Gamma=0.8$, green). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (purple) from
  equation~\eqref{eq:tgrow_min}.}
\end{figure}

>>>>

Also clear from our results are that black holes accreting in AGN phase cannot be accreting in a steady

@@

\begin{figure}
\includegraphics[width=\columnwidth]{bh_growth.eps}
\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
  ($\Gamma=0.8$, green). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (purple) from
  equation~\eqref{eq:tgrow_min}. {\bf BDM: add Compton and Ia heating lines!}}
\end{figure}
